---
title: "Demo: patched with quartofix2()"
vignette: >
  %\VignetteIndexEntry{Demo: patched with quartofix2()}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

This article shows every element `quartofix::quartofix2()` restores by
re-rendering the `.qmd` source with Quarto and splicing the genuine nodes
into pkgdown's HTML after `pkgdown::build_site()`. Compare with the
[raw pkgdown output](quartofix-none.html) or the same article
[patched with `quartofix()`](quartofix.html) instead.

## Callouts

::: {.callout-note}
Callouts like this one keep their default title ("Note") and are recovered
exactly - type, icon, and color included.
:::

::: {.callout-tip}
## This one has a custom title
pkgdown's render loses the callout *type* along with a custom title like
this one - `quartofix()` recovers it anyway by reading the `.qmd` source
that produced this page and matching callouts positionally.
:::

::: {.callout-warning}
`quartofix()` only rewrites the *first* paragraph's default title. A
callout title spanning multiple lines is not currently supported.
:::

::: {.callout-caution}
Running `quartofix()` more than once is safe - already-patched files are
detected and skipped.
:::

::: {.callout-important}
`quartofix()` must run after `pkgdown::build_site()`, not before - it
patches the *rendered* HTML, not the `.qmd` source.
:::

## Tabsets

That doesn't run the code:

::: {.panel-tabset}
## R

```r
pkgdown::build_site()
quartofix::quartofix()
```

## Shell

```sh
Rscript -e 'pkgdown::build_site(); quartofix::quartofix()'
```
:::

That runs the (R) code:

::: {.panel-tabset}
## R

```{r}
1+1
```

## Shell

```sh
Rscript -e 'pkgdown::build_site(); quartofix::quartofix()'
```
:::

## Code annotations

```{r}
#| eval: false
pkgdown::build_site()     # <1>
quartofix::quartofix()    # <2>
```
1. Builds the site as usual - Quarto articles render with callouts,
   tabsets, and annotations all degraded.
2. Walks `docs/`, restores callout markup, and links in the small
   `quartofix.css`/`quartofix.js` bundle wherever it's needed.

## A normal blockquote

Here is an ordinary blockquote, to show it's still intact:

> Premature optimization is the root of all evil.
>
> --- Donald Knuth
